Constraining Black Hole Growth with High-z Quasar Observations

### 2022-08-07 ms.tex
version0806; complete before k send to collegues

\usepackage{bigints}
\usepackage{CJK}

@@

Extrapolation of this argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current capability for
high-$z$ quasar observations \citep{2013ApJ...768..105M,2016ApJ...829...33Y,2019ApJ...884...30W,2019BAAS...51c.121F}.
% \red{KI: you could find better reference in this Decadal Survey?}.
Nevertheless, currently the $z\sim 6$ quasar population is well constrained by multiband surveys
\citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2016ApJ...833..222J,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D}
along with the quasar luminosity function \citep[e.g.,][]{2018ApJ...869..150M}.
%and the virial BH mass estimates
%from the \ion{Mg}{2} 2798 $\rm{\AA}$ line width 
%where 
Deep spectroscopic observations of high-$z$ quasars enable us to measure the virial BH mass 
with the \ion{Mg}{2} single-epoch method and bring insights of the mass distribution
\citep{2007AJ....134.1150J,2007ApJ...669...32K,2010AJ....140..546W,2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}. 
Moreover, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
e.g., the Roman Space Telescope (RST) and Euclid,
infrared imaging and spectroscopic observations will unveil a wealth of information on the
high-$z$ quasar properties and their environments 
\citep{2019BAAS...51c..45R, 2019arXiv190205569A, 2011arXiv1110.3193L}. 
Deep surveys of high-$z$ quasars and their host galaxies will shed light on the early BH evolution, 
also help answering the intriguing questions e.g., 
the existence of supermassive BHs in the early universe within one billion year 
\citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}, 
and the establishment of BH-galaxy coevolution 
\citep[e.g.,][]{2013ApJ...773...44W,2017ApJ...851L...8V,2021ApJ...914...36I,2022ApJ...927..237I,2022MNRAS.511.3751H}.

@@

To determine the initial conditions of the early BH assembly,
the formation pathway of seed BHs has been extensively investigated by numerical simulations and semi-analytical studies
%Formation of seed BHs is the starting point to characterize the early assembly of massive BH populations.
%Their formation pathway and expected mass range have been extensively investigated by numerical simulations and
%semi-analytical studies
\citep{2006MNRAS.370..289B,2009ApJ...696.1798T,2012MNRAS.422.2051N,2014ApJ...781...60H,
2015MNRAS.448..568H,2018MNRAS.474.3825V,2021MNRAS.506..613S,2022arXiv220614459T}.
Massive star formation episodes in the early universe is substantially modulated by external environmental effects such as
(i) H$_2$ photo-dissociating irradiation from nearby galaxies
\citep{2001ApJ...546..635O,2002ApJ...569..558O,2003Natur.425..812B,2010MNRAS.402.1249S,2014MNRAS.445..544S,2014MNRAS.445..107V,2016ApJ...832..134C},
(ii) supersonic baryonic streaming motion that delays gas collapse in halos
\citep{2012MNRAS.424.1335F, 2014MNRAS.439.1092T, 2018ApJ...855...17H,2017MNRAS.471.4878S,2018MNRAS.479.4017I},
and (iii) dynamical heating caused by frequent halo mergers and turbulence injection led by cold accretion flows
\citep{2003ApJ...592..645Y,2010Natur.466.1082M,2015ApJ...810...51M,2019Natur.566...85W,2022Natur.607...48L}.
Those effects keep isothermal collapse ($T\sim 8000~{\rm K}$) of massive gas at high accretion rates of $\gtrsim 0.1~\Msunyr$
without vigorous fragmentation \citep{2014MNRAS.445L.109I,2015MNRAS.446.2380B,2016PASA...33...51L},
and allow supermassive stars with $\sim 10^5~\Msun$ (presumably seed BHs) to form at the halo centers 
\citep{2013ApJ...778..178H,2013A&A...558A..59S,2019PASA...36...27W,2022arXiv220614459T}.
Although the conditions required for heavy seed formation are thought to be too stringent to be realized in the typical regions of the early universe
\citep{2008MNRAS.391.1961D,2009ApJ...695.1430A,2015MNRAS.450.4350I},
recent studies by \citet{2021MNRAS.503.5046L} and \citet{2021ApJ...917...60L} found that the heavy-seed formation
can be accelerated in the rare, overdense regions of the universe, where non-linear galaxy clustering boosts the irradiation intensity
and the frequency of halo mergers.
As a result, \citet{2021ApJ...917...60L} predicted a top-heavy mass distribution of seed BHs ranging from $10^2-10^5~\Msun$.

@@

%%%%%%%
%    Fig. 1
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{seedBHMF_z.pdf}
\caption{
Mass distribution of seed BHs formed in quasar host galaxies at different redshifts ($50\lesssim z \lesssim 10$).
%Each panel includes a redshift span of 10, 
In each panel, the cumulative number distribution of BHs are shown and 
the contribution from newly-born BHs at the redshift interval are denoted with the hatched region.
%with the newly formed BHs denoted by the hatched regions, 
%and the cumulative BHs formed previously by the blue region.
The majority of seed BHs form in the epoch of $40\lesssim z \lesssim 20$.
%The most vigorous seed formation epoches are in redshift ranges $z\sim$ $40-30$ and $30-20$.
Overall, the seed BH mass distribution is extended to $M_\bullet \gtrsim 10^5~\Msun$, 
imprinted with various pathways of parent halo assembly and environmental effects as discussed in \S\ref{sec:seed}.
}
\label{fig:seedmf}
\end{figure*}

@@

\subsection{BH mass growth}
\label{sec:model}
% The BH accretion at high redshifts is probed only by snapshots, in their most luminous quasar phase. 
% We have constraints on simulations and observations of lower redshift counterparts.
With BH seeds planted, we grow the BHs with a semi-analytical accretion rate model and study the evolution of the BH mass distribution until $z=6$. 
\blue{(references + discussion)}
The growth model is characterized by a minimal number of free parameters, 
% the quasar accretion is episodic with Eddington ratio variations,
describing the BH mass growth rate $\Mdot$ by
%%%%%%%
%    Eq. 1
%%%%%%%
% \begin{equation*}
%   \label{eq:mdot_1}
%   \Mdot_\bullet = \frac{\lambda f(\Mbh) \Mbh}{t_{\rm S}} ,
% \end{equation*}
\begin{equation}
  \label{eq:mdot}
  \Mdot_\bullet = \lambda f(\Mbh) \Mdot_\mathrm{Edd} ,
\end{equation}
% where $t_{\rm S} = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
where $\lambda \equiv L/L_\mathrm{Edd}$ is the Eddington ratio,
and $\Mdot_\mathrm{Edd} \equiv L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with a radiative efficiency of $\eta_0=0.1$ \citep{1973A&A....24..337S},
%Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $,
%according to the thin accretion disk model \citep{1973A&A....24..337S}, 
which is consistent with the value obtained from the Soltan's argument \citep[e.g.,][]{2002MNRAS.335..965Y,2010ApJ...725..388C}.
% The high mass BH should be strangulated by as it grows, 
On the basis of studies on the mass dependence of the radiative efficiency for AGNs at $z\lesssim$ 3 
\citep{2008MNRAS.390..561C,2012ApJ...749..187L,2014ApJ...786..104U}, 
we introduce a similar functional form that characterizes its mass dependence 
%
\begin{equation}
f(\Mbh) = \frac{2}{1+\left(\Mbh /M_{\bullet,c} \right)^\delta}, 
\end{equation}
%
where $M_{\bullet,c}=10^8~\Msun$ is adopted.
With a positive value of $\delta$, the BH growth at the high mass end is suppressed, 
while for small BHs the growth rate is accelerated.
%  \blue{(references, Ueda+14?s)}.
In the limit of $\delta \ll 1$, where $f(\Mbh) \simeq 1$ is approximated independent of $M_{\bullet,c}$, the model reproduces an exponential growth with an $e$-folding timescale of
$t_{\rm S} =  \Mbh/\Mdot_{\mathrm{Edd}} \approx 45$ Myr, well known as the Salpeter timescale \citep{1964ApJ...140..796S}.
%h independent of BH mass.
% In \S~\ref{sec:fitting}, $\delta$ turns out to be close to 0, indicating an exponential grow manner independent of BH mass.
%Then $t_{\rm S} =  M/\Mdot_{\mathrm{Edd}} \approx 45$ Myr is the Salpeter $e$-folding timescale \citep{1964ApJ...140..796S}.

@@

For the two cases, the best-fit solutions consistently show a small values of $\delta < 0.01$.
%, which is sufficiently small and should be marginalized out. 
This suggests that in our model assumption, a nearly exponential BH growth pattern is favored. 
% In other words, on average the BH growth can be described as exponential, 
% under the premise that the gas supply is episodical. 
The typical duration of quasar activity is required to be $\tlife \simeq 29$ Myr for both the cases, 
which is $\sim 64\%$ of the $e$-folding time for an exponential growth.
This suggests that accreting seed BHs vary their growth speeds (i.e., the Eddington ratio) 
$\sim 30$ times on average, toward the cosmic time of $t_{\rm H} \gtrsim 900$ Myr at $z\simeq 6$.
The timescale of $\tlife$ also gives a lower bound of the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
which are estimated by the measurement of the physical extents of hydrogen Ly$\alpha$ proximity zones 
observed in the rest-frame UV spectra (e.g., Eilers+2018, Davies+ 2019).\red{KI: we need to figure out 
if their $t_Q$ is the quasar age or lifetime, or something else?}
More detailed comparison is discussed in \S\ref{sec:evol}.

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{tau.png}
\caption{
Left panel: BHMF at $z=$ 6 calculated in the $\fseed=0.01$ case, 
with different $\tlife=$ 10, 18 (the best-fit value), and 50 Myr, respectively, 
and other parameters are fixed to the best-fit values. 
The blue curve denotes the BHMF constrained by the \citetalias{2010AJ....140..546W} result. 
With lower(higher) $\tlife$ than the best-fit value, the BHMF is under(over)-produced in the high mass end.
Right panel: QLF at $z=$ 6 calculated with the same parameters as in the left panel.
The overlaid blue dots are from the \citetalias{2018ApJ...869..150M} $z\sim$ 6 quasar observation. 
With $\tlife$ values different from the best-fit value, the consequent QLF show 
similar trends of deviation from observation as in the BHMF curves.
}
\label{fig:tau}
\end{figure*}

@@

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{BHMF_rhoz.png}
\caption{
{\it Left panel}: BH mass functions at different redshifts of $6\leq z \leq 10$.
The solid lines denote modeled BHMF produced by the best-fit parameters 
and the shaded regions present the $1\sigma$ spread. 
{\it Right panel}: the redshift evolution of the cumulative mass density of BHs with $\Mbh \geq 10^7~\Msun$ in a comoving volume, 
evaluated by the integration of the BHMF shown in the left panel.
The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.8$.
}
\label{fig:BHMF_rhoz}
\end{figure*}

\begin{table}
\renewcommand\thetable{1} %! fix indexing
\caption{$\rho_\bullet(z)$ Evolution Parameters}
\begin{center}
% \tablenum{1}
\begin{tabular}{l c r}
\hline
$M_{\rm min}$ & $\log \rho_{\bullet,0}$ & $k_{\rm M}$ ~~~ \\ 
\hline 
\hline
10$^7$  &  $-5.91\pm 0.28$  &  $-0.58 \pm 0.21$  \\
10$^8$  &  $-6.93\pm 0.47$  &  $-0.78 \pm 0.31$  \\
% 10$^9$  &  $-8.30_{-0.47}^{+0.47}$  & $-1.04_{-0.58}^{+0.54}$ \\
10$^9$  &  $-8.30\pm 0.47$  &  $-1.04 \pm 0.58$ \\
\hline 
\end{tabular}
\label{tab:MFz}
\end{center}
\end{table}

@@

@@

Next, we show the QLFs at different redshifts of $z=6-10$ taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
%The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
\red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
Also, you could compare your results with Aaron Yung's results.}
In the right panel of Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26$ as a function of redshift.
The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
A rapid decay of the quasar number density toward higher redshifts is found by previous studies \citep[e.g.,][]{2001AJ....122.2833F,2016ApJ...833..222J},
which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
%a steeper decline ifts is suggested in recent studies of $z\gtrsim 6$ quasars,
%e.g. \citet{2019ApJ...884...30W} measure the spatial density of $z\sim 6.7$ quasars,
%and fit the parameter $k_{\rm L}=-0.78$ by connecting the $z\sim 6$ result from \citet{2016ApJ...833..222J}.
The rapid decline toward higher redshifts is nicely characterized by the treatment of episodic natures of BH accretion with a finite value of
$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
\citep[e.g.,][]{2010ApJ...718..231S}.
%Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
%interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
%while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
%In our work, we argue that the episodical BH accretion with bursts and quiescent phases is 
%important in matching the $z\sim 6$ quasar observations, 
%and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{QLF_rhoz.png}
\caption{
{\it Left panel}: quasar luminosity functions at different redshifts of $6\leq z \leq 10$. 
The solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
{\it Right panel}: the redshift evolution of the cumulative number density of quasars with $\Muv <-26~{\rm mag}$ in a comoving volume,
evaluated by the integration of the QLF shown in the left panel.
The evolutionary trend can be approximated as $n(\Muv<-26~{\rm mag})\propto 10^{k_{L} z}$, where $k_L \simeq -0.95$.
This result indicates rapid decline of the number of bright quasars toward higher redshifts, consistent with previous observations
\citep[red data points; see][]{2016ApJ...833..222J, 2019ApJ...884...30W}
}
\label{fig:QLF_rhoz}
\end{figure*}

>>>>

\usepackage{bigints}
\usepackage{CJK}
\usepackage{lipsum}

@@

Extrapolation of this argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current capability for
high-$z$ quasar observations \citep{2013ApJ...768..105M,2016ApJ...829...33Y,2019ApJ...884...30W,2019BAAS...51c.121F}.
% \red{KI: you could find better reference in this Decadal Survey?}.
Nevertheless, currently the $z\sim 6$ quasar population is well constrained by multiband surveys
\citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2016ApJ...833..222J,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D}
along with the quasar luminosity function \citep[e.g.,][]{2015ApJ...798...28K,2018ApJ...869..150M}.
%and the virial BH mass estimates
%from the \ion{Mg}{2} 2798 $\rm{\AA}$ line width 
%where 
Deep spectroscopic observations of high-$z$ quasars enable us to measure the virial BH mass 
with the \ion{Mg}{2} single-epoch method and bring insights of the mass distribution
\citep{2007AJ....134.1150J,2007ApJ...669...32K,2010AJ....140..546W,2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}. 
Moreover, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
e.g., the Roman Space Telescope (RST) and Euclid,
infrared imaging and spectroscopic observations will unveil a wealth of information on the
high-$z$ quasar properties and their environments 
\citep{2019BAAS...51c..45R, 2019arXiv190205569A, 2011arXiv1110.3193L}. 
Deep surveys of high-$z$ quasars and their host galaxies will shed light on the early BH evolution, 
also help answering the intriguing questions e.g., 
the existence of supermassive BHs in the early universe within one billion year 
\citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}, 
and the establishment of BH-galaxy coevolution 
\citep[e.g.,][]{2013ApJ...773...44W,2017ApJ...851L...8V,2021ApJ...914...36I,2022ApJ...927..237I,2022MNRAS.511.3751H}.

@@

To determine the initial conditions of the early BH assembly,
the formation pathway of seed BHs has been extensively investigated by numerical simulations and semi-analytical studies
%Formation of seed BHs is the starting point to characterize the early assembly of massive BH populations.
%Their formation pathway and expected mass range have been extensively investigated by numerical simulations and
%semi-analytical studies
\citep{2006MNRAS.370..289B,2009ApJ...696.1798T,2012MNRAS.422.2051N,2014ApJ...781...60H,
2015MNRAS.448..568H,2018MNRAS.474.3825V,2021MNRAS.506..613S,2022arXiv220614459T,2022arXiv220505717B}.
Massive star formation episodes in the early universe is substantially modulated by external environmental effects such as
(i) H$_2$ photo-dissociating irradiation from nearby galaxies
\citep{2001ApJ...546..635O,2002ApJ...569..558O,2003Natur.425..812B,2010MNRAS.402.1249S,2014MNRAS.445..544S,2014MNRAS.445..107V,2016ApJ...832..134C},
(ii) supersonic baryonic streaming motion that delays gas collapse in halos
\citep{2012MNRAS.424.1335F, 2014MNRAS.439.1092T, 2018ApJ...855...17H,2017MNRAS.471.4878S,2018MNRAS.479.4017I},
and (iii) dynamical heating caused by frequent halo mergers and turbulence injection led by cold accretion flows
\citep{2003ApJ...592..645Y,2010Natur.466.1082M,2015ApJ...810...51M,2019Natur.566...85W,2022Natur.607...48L}.
Those effects keep isothermal collapse ($T\sim 8000~{\rm K}$) of massive gas at high accretion rates of $\gtrsim 0.1~\Msunyr$
without vigorous fragmentation \citep{2014MNRAS.445L.109I,2015MNRAS.446.2380B,2016PASA...33...51L},
and allow supermassive stars with $\sim 10^5~\Msun$ (presumably seed BHs) to form at the halo centers 
\citep{2013ApJ...778..178H,2013A&A...558A..59S,2019PASA...36...27W,2022arXiv220614459T}.
Although the conditions required for heavy seed formation are thought to be too stringent to be realized in the typical regions of the early universe
\citep{2008MNRAS.391.1961D,2009ApJ...695.1430A,2015MNRAS.450.4350I},
recent studies by \citet{2021MNRAS.503.5046L} and \citet{2021ApJ...917...60L} found that the heavy-seed formation
can be accelerated in the rare, overdense regions of the universe, where non-linear galaxy clustering boosts the irradiation intensity
and the frequency of halo mergers.
As a result, \citet{2021ApJ...917...60L} predicted a top-heavy mass distribution of seed BHs ranging from $10^2-10^5~\Msun$.

@@

%%%%%%%
%    Fig. 1
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{seedBHMF_z.png}
\caption{
Mass distribution of seed BHs formed in quasar host galaxies at different redshifts ($50\lesssim z \lesssim 10$).
%Each panel includes a redshift span of 10, 
In each panel, the cumulative number distribution of BHs are shown and 
the contribution from newly-born BHs at the redshift interval are highlighted in magenta.
%with the newly formed BHs denoted by the hatched regions, 
%and the cumulative BHs formed previously by the blue region.
The majority of seed BHs form in the epoch of $40\lesssim z \lesssim 20$.
%The most vigorous seed formation epoches are in redshift ranges $z\sim$ $40-30$ and $30-20$.
Overall, the seed BH mass distribution is extended to $M_\bullet \gtrsim 10^5~\Msun$, 
imprinted with various pathways of parent halo assembly and environmental effects as discussed in \S\ref{sec:seed}.
}
\label{fig:seedmf}
\end{figure*}

@@

\subsection{BH mass growth}
\label{sec:model}
% The BH accretion at high redshifts is probed only by snapshots, in their most luminous quasar phase. 
% We have constraints on simulations and observations of lower redshift counterparts.
With BH seeds planted, we grow the BHs with a semi-analytical accretion rate model and study the evolution of the BH mass distribution until $z=6$. 
% \blue{(references + discussion)}
The growth model is characterized by a minimal number of free parameters, 
% the quasar accretion is episodic with Eddington ratio variations,
describing the BH mass growth rate $\Mdot$ by
%%%%%%%
%    Eq. 1
%%%%%%%
% \begin{equation*}
%   \label{eq:mdot_1}
%   \Mdot_\bullet = \frac{\lambda f(\Mbh) \Mbh}{t_{\rm S}} ,
% \end{equation*}
\begin{equation}
  \label{eq:mdot}
  \Mdot_\bullet = \lambda f(\Mbh) \Mdot_\mathrm{Edd} ,
\end{equation}
% where $t_{\rm S} = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
where $\lambda \equiv L/L_\mathrm{Edd}$ is the Eddington ratio,
and $\Mdot_\mathrm{Edd} \equiv L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with a radiative efficiency of $\eta_0=0.1$ \citep{1973A&A....24..337S},
%Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $,
%according to the thin accretion disk model \citep{1973A&A....24..337S}, 
which is consistent with the value obtained from the Soltan's argument \citep[e.g.,][]{2002MNRAS.335..965Y,2010ApJ...725..388C}.
% The high mass BH should be strangulated by as it grows, 
On the basis of studies on the mass dependence of the radiative efficiency for AGNs at $z\lesssim$ 3 
\citep{2008MNRAS.390..561C,2012ApJ...749..187L,2014ApJ...786..104U}, 
we introduce a similar functional form that characterizes its mass dependence 
%
\begin{equation}
f(\Mbh) = \frac{2}{1+\left(\Mbh /M_{\bullet,c} \right)^\delta}, 
\end{equation}
%
where $M_{\bullet,c}=10^8~\Msun$ is adopted.
With a positive value of $\delta$, the BH growth at the high mass end is suppressed, 
while for small BHs the growth rate is accelerated.
%  \blue{(references, Ueda+14?s)}.
In the limit of $\delta \ll 1$, where $f(\Mbh) \simeq 1$ is approximated independent of $M_{\bullet,c}$, the model reproduces an exponential growth with an $e$-folding timescale of
$t_{\rm S} =  \Mbh/\Mdot_{\mathrm{Edd}} \approx 45$ Myr, well known as the Salpeter timescale \citep{1964ApJ...140..796S}.
%h independent of BH mass.
% In \S~\ref{sec:fitting}, $\delta$ turns out to be close to 0, indicating an exponential grow manner independent of BH mass.
%Then $t_{\rm S} =  M/\Mdot_{\mathrm{Edd}} \approx 45$ Myr is the Salpeter $e$-folding timescale \citep{1964ApJ...140..796S}.

@@

For the two cases, the best-fit solutions consistently show a small values of $\delta < 0.01$.
%, which is sufficiently small and should be marginalized out. 
This suggests that in our model assumption, a nearly exponential BH growth pattern is favored. 
% In other words, on average the BH growth can be described as exponential, 
% under the premise that the gas supply is episodical. 
The typical duration of quasar activity is required to be $\tlife \simeq 29$ Myr for both the cases, 
which is $\sim 64\%$ of the $e$-folding time for an exponential growth.
This suggests that accreting seed BHs vary their growth speeds (i.e., the Eddington ratio) 
$\sim 30$ times on average, toward the cosmic time of $t_{\rm H} \gtrsim 900$ Myr at $z\simeq 6$.
The timescale of $\tlife$ also gives a lower bound of the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
which are estimated by the measurement of the physical extents of hydrogen Ly$\alpha$ proximity zones 
observed in the rest-frame UV spectra \citep[e.g.,][]{2018ApJ...867...30E,2019ApJ...884L..19D}.
% \red{KI: we need to figure out if their $t_Q$ is the quasar age or lifetime, or something else?}
More detailed comparison is discussed in \S\ref{sec:evol}.

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{tau.png}
\caption{
Left panel: BHMF at $z=$ 6 calculated in the $\fseed=0.01$ case, 
with different $\tlife=$ 10, 18 (the best-fit value), and 50 Myr, respectively, 
and other parameters are fixed to the best-fit values. 
The blue curve denotes the BHMF constrained by the \citetalias{2010AJ....140..546W} result. 
With lower(higher) $\tlife$ than the best-fit value, the BHMF is under(over)-produced in the high mass end.
Right panel: QLF at $z=$ 6 calculated with the same parameters as in the left panel.
The overlaid blue dots are from the \citetalias{2018ApJ...869..150M} $z\sim$ 6 quasar observation. 
With $\tlife$ values different from the best-fit value, the consequent QLF show 
similar trends of deviation from observation as in the BHMF curves.
}
\label{fig:tau}
\vspace{4mm}
\end{figure*}

@@

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{BHMF_rhoz.png}
\caption{
{\it Left panel}: BH mass functions at different redshifts of $6\leq z \leq 10$.
The solid lines denote modeled BHMF produced by the best-fit parameters 
and the shaded regions present the $1\sigma$ spread. 
{\it Right panel}: the redshift evolution of the cumulative mass density of BHs with $\Mbh \geq 10^7~\Msun$ in a comoving volume, 
evaluated by the integration of the BHMF shown in the left panel.
The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.68$.
}
\label{fig:BHMF_rhoz}
\vspace{4mm}
\end{figure*}

@@

%%%%%%%
%    Table. 1 
%%%%%%%
\begin{table}
\renewcommand\thetable{1} %! fix indexing
\caption{$\rho_\bullet(z)$ Evolution Parameters}
\begin{center}
% \tablenum{1}
\begin{tabular}{l c r}
\hline
\hline
$M_{\rm min}$ & $\log \rho_{\bullet,0}$ & $k_{\rm M}$ ~~~ \\ 
\hline 
10$^7$  &  $ 1.81\pm 0.28$  &  $-0.68 \pm 0.21$  \\
10$^8$  &  $ 1.54\pm 0.47$  &  $-0.84 \pm 0.31$  \\
% 10$^9$  &  $-8.30_{-0.47}^{+0.47}$  & $-1.04_{-0.58}^{+0.54}$ \\
10$^9$  &  $ 1.01\pm 0.47$  &  $-1.01 \pm 0.58$ \\
\hline 
\end{tabular}
\label{tab:MFz}
\end{center}
\end{table}

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{QLF_rhoz.png}
\caption{
{\it Left panel}: quasar luminosity functions at different redshifts of $6\leq z \leq 10$. 
The solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
{\it Right panel}: the redshift evolution of the cumulative number density of quasars with $\Muv <-26~{\rm mag}$ in a comoving volume,
evaluated by the integration of the QLF shown in the left panel.
The evolutionary trend can be approximated as $n(\Muv<-26~{\rm mag})\propto 10^{k_{L} z}$, where $k_L \simeq -0.96$.
This result indicates rapid decline of the number of bright quasars toward higher redshifts, consistent with previous observations
\citep[red data points; see][]{2016ApJ...833..222J, 2019ApJ...884...30W}
}
\label{fig:QLF_rhoz}
\vspace{5mm}
\end{figure*}

@@

Next, we show the QLFs at different redshifts of $z=6-10$ taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
Similar to the BHMF, for all the redshift range, the shape of the QLF is well approximated with a double power-law function.
From higher to lower redshifts, the number density of luminous quasars increases and the bright-end of the distribution is extended.
% %The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
% \red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
% Also, you could compare your results with Aaron Yung's results.}
In the right panle of Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26~{\rm mag}$ as a function of redshift.
The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
A rapid decay of the quasar number density toward higher redshifts is found by previous studies \citep[e.g.,][]{2001AJ....122.2833F,2016ApJ...833..222J},
which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
%a steeper decline ifts is suggested in recent studies of $z\gtrsim 6$ quasars,
%e.g. \citet{2019ApJ...884...30W} measure the spatial density of $z\sim 6.7$ quasars,
%and fit the parameter $k_{\rm L}=-0.78$ by connecting the $z\sim 6$ result from \citet{2016ApJ...833..222J}.
The rapid decline toward higher redshifts is nicely characterized by the treatment of episodic natures of BH accretion with a finite value of
$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
\citep[e.g.,][]{2010ApJ...718..231S}.
%Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
%interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
%while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
%In our work, we argue that the episodical BH accretion with bursts and quiescent phases is 
%important in matching the $z\sim 6$ quasar observations, 
%and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.

%On the other hand, the statistics of BH masses together with the ERDF in their growth history can rebuild quasar luminosity functions across cosmic time,
%which is interesting to be probed with future observations.
In Fig.~\ref{fig:LFs}, we divide the cosmological QLF into four different epochs; (a) $z\simeq 7$, (b) $z\simeq 8$, (c) $z\simeq 9$, and (d) $z\simeq 10-13$.
The black solid and dashed curves present the QLF for the unobscured population (i.e., type-I AGNs, same as those in Fig.~\ref{fig:QLF_rhoz})
and the whole population (i.e., type-I and type-II AGNs).
We note that the AGN obscured fraction based on X-ray samples \citep{2014ApJ...786..104U} is applied to faint objects, 
but the correction factor is highly uncertain at the faint end of $\Muv\gtrsim -20$ mag.
% sampled in \citet{2014ApJ...786..104U},
%we emphasize that the observed (Type I) QLF after the current obscuration prescription can be highly uncertain in the faint end,
%ßwhich is to be improved by the future equipments.
% More thorough studies on the high-$z$ quasar obscuration by upcoming equipments will improve the understanding on this aspect.
%We also produce the intrinsic (Type I and Type II) luminosity function without obscuration effects.
%The QLF emgerging from high redshifts quickly evolves toward brighter luminosity 
%with the number of quasars increases as BHs grow.
We also overlay the expected depths and volumes of upcoming survey programs (blue lines) with Wide Euclid \citep{2011arXiv1110.3193L}
and Wide RST \citep{2019arXiv190205569A}.
Table.~\ref{tab:N_detect} summarizes the expected number of detected quasars in each survey. 
Euclid will identify quasars up to $z\sim 8$ and discover $O(100-1000)$ quasars at $z\simeq 7-8$.
The RST will be able to explore the very faint ($\Muv>-22$ mag) but abundant quasar population even at $z>10$, in principle,
after subtracting galaxy contaminants.

%will be crucial to construct the LF data for high-$z$ quasars and galaxies,
%categorizing them by spectroscopic diagnostics.
%We show the detection limit of these surveys at each redshift in Fig.~\ref{fig:LFs},
%demonstrating their capability of optimizing high-$z$ galaxy and quasar observations.
%The adopted survey parameters is shown in Table.~\ref{tab:N_detect}.
%The depths of detection will be pushed down to $\Muv\lesssim -20$,
%which is able to uncover the critical luminosities at which the numbers of galaxies and quasars are comparable.
%The number of high-$z$ quasars are also predicted at each redshift (Table.~\ref{tab:N_detect}),
%with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
%The large sample of objects at those high redshifts will shed light on
%the early coevolution of galaxies and BHs in a statistically unbiased way.
